Naturalness in U(1) extensions of the MSSM

### 2015-01-20 paper/e6ssm-tuning-paper.tex
Fixed a paragraph that had been missed in editing.  Added reference to table that we need to include.

To further illustrate this point we looked at how the tuning compares
for low tuning benchmarks in the MSSM and E6SSM when the highscale
boundary condition, $M_X$ is raised. The results of this are shown in
Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is a quite complicated
we now discuss these in detail as it provides some insight into the
many differences in the tuning between the two models.

In the top left panel one can see that the MSSM tuning (green)
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the top right confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top left panel. In thus case we have chosen a
point with large mixing which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall fo the points we looked at.

The E$_6$SSM tunings are rather more complicated as there are more
sources of fine tuning.  By comparing them to the MSSM tuning one can
see that the scale at which the parameters are defined is very
important for determining which point is more fine tuned.  In the
bottom left panel one can see that the dependence of the E$_6$SSM
tuning on the cutoff is rather complicated, illustrating that any
statement about which model is more tuned depends on the cutoff scale
considered.

>>>>

To further illustrate this point we looked at how the tuning compares
for low tuning benchmarks in the MSSM and E6SSM when the highscale
boundary condition, $M_X$ is raised. These benchmarks are defined in
table \ref{} and the results are shown in
Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is a quite complicated
we now discuss these in detail as it provides some insight into the
many differences in the tuning between the two models.

In the top left panel one can see that the MSSM tuning (green)
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the top right confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top left panel. In thus case we have chosen a
point with large mixing which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall for the points we looked at.

Comparing the MSSM tuning to the E$_6$SSM tunings one can see that
which point is more fine tuned depends on the scale at which the
parameters are defined.  This illustrates that any statement about which
model is more tuned depends on the cutoff scale considered.
